Anomalous waves triggered by abrupt depth changes: experimental measurements and deterministic-statistical truncated KdV theory

### 2019-10-02 paper2_JNLS/paper.tex
NM

\title{The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes}

% Title ideas
% Could include words "theory and experiments".
%Old idea: Deterministic and statistical truncated KdV models for anomalous waves induced by abrupt depth change
\author{
C.~Tyler Bolles\thanks{University of Michigan},
Andrew J.~Majda\thanks{Courant Institute of Mathematical Sciences}, 
M.~N.~J.~Moore\thanks{Florida State University}, 
Di Qi\thanks{Courant Institute of Mathematical Sciences} }
\maketitle

\begin{abstract} 
Recent laboratory experiments revealed the emergence of anomalous statistics in a randomized surface waves upon encountering an abrupt depth change (ADC) in the bottom topography (Bolles et al. PRF 2019). Majda et al.~2019 established a theoretical foundation, based on analysis of the truncated KdV (TKdV) equations, that successfully captures several key qualitative features of the experiments, including the robust emergence of anomalous statistics. The framework exploits the Hamiltonian structure of TKdV to construct invariant measures that are statistical matched at the ADC, and is corroborated by simulations of the deterministic dynamics. 
%
Here we present a more comprehensive treatment of these parallel experimental and modeling efforts, with emphasis on the link between the two. We present an assortment of new experimental measurements and carefully compare them to model predictions. We establish a more precise link between experimental and model parameters, so that the invariant measure underlying the model can be calibrated to the specific conditions present in these experiment, as well as others. The model predicts a peculiar relationship between surface-displacement skewness and surface-slope variance, which is confirmed in spectacular fashion by direct experimental measurements.
\end{abstract}

%Here, we present a more comprehensive treatment of the experimental and modeling efforts in conjunction with on another. We report new experimental measurements and new theoretical results, with a detailed comparison between the two.

>>>>

\title{Anomalous waves triggered by abrupt depth changes: experimental measurements and deterministic-statistical truncated KdV theory}

% ORIGINAL: The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes
% Words: triggered, induced, generated, sparked

\author{
C.~Tyler Bolles\thanks{University of Michigan},
Andrew J.~Majda\thanks{Courant Institute of Mathematical Sciences}, 
M.~N.~J.~Moore\thanks{Florida State University}, 
Di Qi\thanks{Courant Institute of Mathematical Sciences} }
\maketitle

\begin{abstract} 
Recent laboratory experiments revealed the emergence of anomalous statistics in a randomized surface waves upon encountering an abrupt depth change (ADC) in the bottom topography (Bolles et al. PRF 2019). Majda et al.~2019 established a theoretical foundation, based on analysis of the truncated KdV (TKdV) system, that successfully captures several key qualitative features of the experiments including the robust emergence of anomalous statistics. The framework exploits the Hamiltonian structure of TKdV to construct invariant measures that are statistical matched at the ADC, and is corroborated by simulations of the deterministic dynamics. 
%
Here we present a more comprehensive treatment of these parallel experimental and modeling efforts, with emphasis on the link between the two. We present an assortment of new experimental measurements and carefully compare them to model predictions. We establish a more precise link between experimental and model parameters, so that the invariant measure underlying the model can be calibrated to the specific conditions present in experiments. The model predicts a peculiar relationship between surface-displacement skewness and surface-slope variance, which is confirmed in spectacular fashion by direct experimental measurements.
\end{abstract}
